\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-11-19 Proposal.tex
adding changes fromthe meeting

\documentclass[twoside]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.5} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF

@@

-addresses fellow experts from your field (but not from your particular topic of research). 
- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.
  (target size: 1 page)
\newpage
  \section{Statement and Motivation of Research}
  This part should make clear which question, exactly, you are
  pursuing, and why your project is relevant/interesting. This is the
  place to cite relevant literature. Where does your project extend
  the state of the art? what weaknesses in known approaches to you
  hope to overcome? If you have carried out preliminary experiments,
  describe them here.

(target size: 3-4 pages)

\subsection{OMDoc}
(half a page)
\vspace*{8cm}
\subsection{Spatial Narration}
What is Prezi?
(half a page)
\vspace*{8cm}
\subsection{Combining OMDoc and Spatial Narration}
What is the idea?
(half a page)
\newpage
\subsection{Positive Effects of the Combination of Spatial Narration and OMDoc}
Why is this important for the world?
How will this improve learning?
(1 page)
\newpage
\subsection{Different Representations of Data}
What's the best representation one could do?
(1 page)
  (target size: 3-5 pages)
\newpage
\section{Planned Investigation}

@@

\subsection{Meaningful Representation of Knowledge Graphs}
(1 page)
\newpage

@@

????

@@

\begin{figure}[h]
\begin{center}
\begin{ganttchart}[y unit title=0.4cm,
y unit chart=0.5cm,
vgrid,hgrid, 
title label anchor/.style={below=-1.6ex},
title left shift=.05,
title right shift=-.05,
title height=1,
bar/.style={fill=gray!50},
incomplete/.style={fill=white},
progress label text={},
bar height=0.7,
group right shift=0,
group top shift=.6,
group height=.3,
group peaks={}{}{.2}]{24}
%labels
\gantttitle{Proposed Timeline}{24} \\
\gantttitle{December}{4} 
\gantttitle{January}{4} 
\gantttitle{February}{4} 
\gantttitle{March}{4} 
\gantttitle{April}{4} 
\gantttitle{May}{4} \\
%tasks
\ganttbar{Preliminary development}{2}{10} \\
\ganttbar{Graph visualization}{11}{16} \\
\ganttbar{Testing \& Performance}{17}{20} \\
\ganttbar{Final Report submission}{21}{21.5}

@@

>>>>

\documentclass[twoside]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
\usepackage[show]{ed}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.5} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF

@@

-addresses fellow experts from your field (but not from your particular topic of research). 
- Here you should technically connect to the main concepts from that field and give an outline of your project, stating the research/engineering question that you want to get answered by your project.

Why is this important for the world?
How will this improve learning?
More effective education.

(target size: 1 page)

\ednote{Include in introduction Statement and Motivation of Research  } 
\newpage 
\section{Preliminaries}
  This part should make clear which question, exactly, you are
  pursuing, and why your project is relevant/interesting. This is the
  place to cite relevant literature. Where does your project extend
  the state of the art? what weaknesses in known approaches to you
  hope to overcome? If you have carried out preliminary experiments,
  describe them here.

(target size: 3-4 pages)
\ednote {explain primitives and apply to prezi.}

\subsection{OMDoc}
(half a page)
\vspace*{8cm}
\subsection{Spatial Narration}
What is Prezi?
(half a page)
\vspace*{8cm}
\subsection{Different Representations of Data}
What's the best representation one could do?
(1 page)

\section{Planned Investigation}

@@

\subsection{Meaningful Representation of Knowledge Graphs}
(1 page)

\ednote{evaluation criteria from lecture slides}
\newpage

\section{Work Plan}
\subsection{WP1: Understand API of Prezi or similar software}

\subsection{WP2: Combining OMDoc and Spatial Narration}

What is the idea?
(half a page)
\newpage
\subsection{WP3: Evaluation}
1. Positive Effects of the Combination of Spatial Narration and OMDoc
2. How fast does this work?
-> qualitative analysis.

(1 page)
\newpage
  (target size: 3-5 pages)
\newpage

@@

\ednote{When do I feel successful?\\
-running system (or I can tell why it didn't/couldn't work) \& \\
-users can understand it and reconstruct the original graph. }

@@

\ednote {wp 4 - thesis writing}

\begin{figure}[h]
\begin{center}
\begin{ganttchart}[y unit title=0.4cm,
y unit chart=0.5cm,
vgrid,hgrid, 
title label anchor/.style={below=-1.6ex},
title left shift=.05,
title right shift=-.05,
title height=1,
bar/.style={fill=gray!50},
incomplete/.style={fill=white},
progress label text={},
bar height=0.7,
group right shift=0,
group top shift=.6,
group height=.3,
group peaks={}{}{.2}]{24}
%labels
\gantttitle{Proposed Timeline}{24} \\
\gantttitle{December}{4} 
\gantttitle{January}{4} 
\gantttitle{February}{4} 
\gantttitle{March}{4} 
\gantttitle{April}{4} 
\gantttitle{May}{4} \\
%tasks
\ganttbar{WP 1}{2}{10} \\
\ganttbar{WP 2}{11}{16} \\
\ganttbar{WP 3}{17}{20} \\
\ganttbar{WP 4}{21}{21.5}

@@

\ednote {
-knowledge representation, semantic web
}
